%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}#2 \vspace{-2pt}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://kreal321.github.io/blog/about-me/}{\Large Kezhen (Kason) Xu}}   & Email: \href{mailto:kezhen\_xu@hotmail.com}{kezhen\_xu@hotmail.com}\\
  \href{https://kreal321.github.io/blog/about-me/}{Personal Website} \textbar \thinspace \thinspace \href{https://www.linkedin.com/in/kezhen-xu/}{LinkedIn} \textbar \thinspace \thinspace \href{https://github.com/Kreal321/}{Github} & Mobile : +1-614-980-1990 \\
  
\end{tabular*}

%-----------Summary-----------------
\section{Summary}
  \resumeSubHeadingListStart
  \item{
    {Highly skilled Java/J2EE Full Stack Developer with 3.5 years of professional experience and over 8 years of
    experience in programming with diversified exposure in all the phases of the Software Development Life Cycle
    using Spring Framwork, Angular, Hibernate ORM, Messaging, Relational and NoSQL databases,
    Microservices architecture, AWS services as well as testing and maintaining enterprise-level web applications.
    Excellent problem-solving skills and a strong ability to work collaboratively in an agile team environment.}
  }
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ohio State University (OSU)}{Columbus, OH}
      {Bachelor of Engineering in Computer Science;  GPA: 3.93}{Jan. 2020 -- Aug. 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Deloitte}{Columbus, OH}
    {Software Engineer, Lead}{Feb 2024 - Present}
    \resumeItemListStart
      \resumeItem{}
        {Spearheaded the migration of an outdated \textbf{Spring Boot microservices architecture}, comprising \textbf{10+} services, to the latest version and successfully resolving \textbf{500+ vulnerabilities}, enhancing the application's security and stability.}
      \resumeItem{}
        {Architected and led the development of a \textbf{Power BI} integration using the \textbf{MongoDB BI Connector} and \textbf{Data Gateway}, eliminating the need for a SQL database and reducing process time by \textbf{50\%}, optimizing data reporting capabilities.}
      \resumeItem{}
        {Integrated latest machine learning algorithms and \textbf{Gen AI} to improve predictive confidence by \textbf{5\%}, using \textbf{Spring Batch} and \textbf{Apache Spark} to boost processing speed by \textbf{60\%}, enhancing overall application performance.}
      \resumeItem{}
        {Directed an agile team of \textbf{10 engineers}, achieving a \textbf{20\%} reduction in project turnaround time by streamlining the ticket record process and implementing more efficient workflows, leading to improved team productivity.}
      \resumeItem{}
        {Administered comprehensive \textbf{code reviews} and provided \textbf{mentorship} to team members, enhancing code quality and improving testing plans. This initiative led to a \textbf{30\%} reduction in post-deployment hotfixes through improved automated testing processes.}
      \resumeItem{Technologies Used}
        {: Java 17, Spring Framework (MVC, AOP, JPA, Security, Batch, Cloud), Azure (VM, DevOps, Blob Storage, AD, SPN), MongoDB, Angular 16/18, RabbitMQ, Microservices, Consul, Docker, Redis, JUnit, Mockito,, MySQL, Agile, Scrum}
    \resumeItemListEnd

    \resumeSubheading
    {Beaconfire Inc.}{East Windsor, NJ}
    {Java Full Stack Developer}{Aug 2022 - Feb 2024}
    \resumeItemListStart
      \resumeItem{}
        {Simplified the codebase by converting an \textbf{XML based Spring} app to a auto-configured \textbf{Spring Boot} app with \textbf{Hibernate}, \textbf{Spring AOP}, and \textbf{Spring Security (JWT)} integration, resulting in a \textbf{50\%} reduction in future maintenance and expansion challenges.}
      \resumeItem{}
        {Structured \textbf{RESTful API} endpoints with versioning for consistency across frontend \textbf{Angular} services and backend \textbf{Spring} controllers, while also implementing security measures like \textbf{Angular Auth Guards} and \textbf{Spring Security} for endpoint protection.}
      \resumeItem{}
        {Skillfully converted a \textbf{Monolithic} application into a \textbf{Microservices architecture} with \textbf{Netflix Eureka}, \textbf{Feign Client} for inter-service communication, and \textbf{RabbitMQ} for asynchronous \textbf{message} delivery, achieving over \textbf{50\%} performance enhancement and reducing the average response time from \textbf{2.4} seconds to an impressive \textbf{0.6 seconds}}
      \resumeItem{}
        {Strengthened unit \textbf{testing} using \textbf{JUnit} and \textbf{Mockito}, refined documentation and standardized \textbf{CI/CD procedures} by \textbf{Gitlab CI}, which drastically lowered change failure rates to under \textbf{6\%}, ensuring smoother development and deployment.}
      \resumeItem{}
        {Collaborated with cross-functional teams and worked in a \textbf{client-facing Agile} team to gather requirements and deliver software solutions on time and within budget, achieving a success rate of \textbf{95\%}.}
      \resumeItem{Technologies Used}
        {: Java 8, Spring Framework (MVC, AOP, JPA, Security), Angular, RabbitMQ, Microservices, Netflix Eureka and Feign Client, AWS (RDS, S3, EC2, Lambda, EKS), Docker, Gitlab CI, JUnit, Mockito, Maven, MySQL, MongoDB, Redis, Jira, Confluence, Agile, Scrum}
    \resumeItemListEnd

    \resumeSubheading
      {Clinical Skills Education and Assessment Center \textbar \thinspace \thinspace OSU}{Columbus, OH}
      {Web Application Developer}{Jan 2022 - May 2022}
      \resumeItemListStart
        \resumeItem{}
          {Led a team of \textbf{4} in utilizing \textbf{Angular} with \textbf{Material Design} to build a user-friendly web interface that catered to non-professionals.}
        \resumeItem{}
          {Developed a customizable task queue with \textbf{drag-and-drop} features to enhance user scenarios and minimize user restrictions, resulting in an enriched and intuitive user experience.}
        \resumeItem{}
          {Created a Raspberry Pi based server for simulation equipment control, using \textbf{WebSocket} for long term frontend-backend communication.}
        \resumeItem{Technologies Used}
          {: Angular, TypeScript, Python, HTML/CSS, WebSocket, Bootstrap 5, Material Design}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
